Super-resolution of Aeromagnetic Survey Data

### 2023-10-12 paper1.tex
Improve figures and tables

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=\linewidth]{fig/p1/rdn.png}
    \caption[The RDN architecture]{The RDN architecture, which acts as the ESRGAN generator.
        Twenty-three Basic Blocks are stacked sequentially to form the main convolution path.
        Upsampling to the target output size is performed after the main convolution sequence.
        Adapted from \textcite{wangESRGANEnhancedSuperresolution2018}.
    }
    \label{fig:rdn}
\end{figure}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=\linewidth]{fig/p1/rdb.png}
    \caption[Basic blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
        ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
        Weight factors are indicated by \(\beta{}\) and \(\gamma{}\).
        Noise injection is not used in RDN\@.
        Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.
    }
    \label{fig:rdb}
\end{figure}

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=0.75\linewidth]{fig/p1/convs.png}
    \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green). LReLU refers to the Leaky-ReLU activation function. Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.}
    \label{fig:convs}
\end{figure}

@@

\begin{table}[hbtp]
    \centering
    \begin{tblr}{
            colspec={
                    r |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                },
            row{1} = {guard}
        }
                & \SetCell[c=2]{c} Bicubic &            & \SetCell[c=2]{c} RDN\textdaggerdbl{} &                 & \SetCell[c=2]{c} ESRGAN+              \\
        \hline{}
                & \(\mu\)                  & \(\sigma\) & \(\mu\)                              & \(\sigma\)      & \(\mu\)                  & \(\sigma\) \\
        RMSE    & 13.545                   & 26.576     & \textbf{7.265}                       & \textbf{13.741} & 11.120                   & 21.670     \\
        SISM    & 0.924                    & 0.047      & \textbf{0.959}                       & \textbf{0.037}  & 0.922                    & 0.054      \\
        MS-SSIM & 0.971                    & 0.018      & \textbf{0.988}                       & \textbf{0.012}  & 0.976                    & 0.020      \\
    \end{tblr}

>>>>

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=\linewidth]{fig/p1/rdn_vec.pdf}
    \caption[The RDN architecture]{The RDN architecture, which acts as the ESRGAN generator.
        Twenty-three Basic Blocks are stacked sequentially to form the main convolution path.
        Upsampling to the target output size is performed after the main convolution sequence.
        Adapted from \textcite{wangESRGANEnhancedSuperresolution2018}.
    }
    \label{fig:rdn}
\end{figure}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=\linewidth]{fig/p1/rdb_vec.pdf}
    \caption[Basic blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
        ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
        Weight factors are indicated by \(\beta{}\) and \(\gamma{}\).
        Noise injection is not used in RDN\@.
        Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.
    }
    \label{fig:rdb}
\end{figure}

\begin{figure}[hbtp]
    \centering
    \includegraphics[width=0.75\linewidth]{fig/p1/convs_vec.pdf}
    \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green). LReLU refers to the Leaky-ReLU activation function. Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.}
    \label{fig:convs}
\end{figure}

@@

\begin{table}[hbtp]
    \centering
    \begin{tblr}{
            colspec={
                    r |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l]
                },
            row{1} = {guard}
        }
                & \SetCell[c=2]{c} Bicubic &            & \SetCell[c=2]{c} RDN\textdaggerdbl{} &                 & \SetCell[c=2]{c} ESRGAN+              \\
        \hline{}
                & \(\mu\)                  & \(\sigma\) & \(\mu\)                              & \(\sigma\)      & \(\mu\)                  & \(\sigma\) \\
        RMSE    & 13.545                   & 26.576     & \textbf{7.265}                       & \textbf{13.741} & 11.120                   & 21.670     \\
        SISM    & 0.924                    & 0.047      & \textbf{0.959}                       & \textbf{0.037}  & 0.922                    & 0.054      \\
        MS-SSIM & 0.971                    & 0.018      & \textbf{0.988}                       & \textbf{0.012}  & 0.976                    & 0.020      \\
    \end{tblr}

### 2023-10-12 paper2.tex
Improve figures and tables

\begin{table}[hbtp]
    \begin{tblr}{
            colspec={
                    r |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                },
            row{1} = {guard}
        }
                         & \SetCell[c=2]{c} Reserved synthetic test &            & \SetCell[c=2]{c} Aeromagnetic grid dataset              \\
        \hline{}
                         & \(\mu\)                                  & \(\sigma\) & \(\mu\)                                    & \(\sigma\) \\
        Baseline model   & 0.9844                                   & 0.0296     & 0.9731                                     & 0.0086     \\
        Fine-tuned model & 0.9838                                   & 0.0329     & 0.9754                                     & 0.0078     \\
    \end{tblr}

>>>>

\begin{table}[hbtp]
    \begin{tblr}{
            colspec={
                    r |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l] |
                    Q[si={table-format=2.3},r]
                    Q[si={table-format=2.3},l]
                },
            row{1} = {guard}
        }
                         & \SetCell[c=2]{c} Reserved synthetic test &            & \SetCell[c=2]{c} Aeromagnetic grid dataset              \\
        \hline{}
                         & \(\mu\)                                  & \(\sigma\) & \(\mu\)                                    & \(\sigma\) \\
        Baseline model   & 0.9844                                   & 0.0296     & 0.9731                                     & 0.0086     \\
        Fine-tuned model & 0.9838                                   & 0.0329     & 0.9754                                     & 0.0078     \\
    \end{tblr}
